Data_visualization

### 2018-09-10 Rmd/Data_visualization_common_names.Rmd
TOTAL_POLLEN

ggplot(tab, aes(x=reorder(species, pollen_ovule_ratio, colour = cut), y=pollen_ovule_ratio))+aes(fill=family)+
  geom_bar(stat="identity", width=0.5)+theme(axis.text.x = element_text(angle = 60, hjust=1))+scale_fill_manual(values=cbPalette)

>>>>

ggplot(tab, aes(x=reorder(species, pollen_ovule_ratio, colour = cut), y=pollen_ovule_ratio))+aes(fill=family)+
  geom_bar(stat="identity", width=0.5)+theme(axis.text.x = element_text(angle = 60, hjust=1))+scale_fill_manual(values=cbPalette)
```
